Publilia-03-survivorship.Rmd

### 2023-08-12 scripts/Publilia-03-survivorship.Rmd
fixed prelim fig saving paths for publilia-03

ggsave("desL.ant_treatment.quad.final.png",
       desL.ant_treatment.quad.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

@@

surv_reg_data.tbl_summary.desL.ant_treatment %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv_reg_data.tbl_summary.desL.ant_treatment.docx")
```

@@

desL.ant_treatment.quad.qb.tbl.merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv.reg_summary.desL.ants_treatment.quad.docx")
```

@@

ggsave("desL.ants_gt2d.quad.final.png",
       desL.ants_gt2d.quad.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

@@

surv_reg_data.tbl_summary.desL.ants_gt2d %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv_reg_data.tbl_summary.desL.ants_gt2d.docx")
```

@@

desL.ants_gt2d.quad.qb.tbl.merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv.reg_summary.desL.ants_gt2d.quad.docx")
```

@@

ggsave("desP.ants_gt2d.quad.final.png",
       desP.ants_gt2d.quad.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

@@

surv_reg_data.tbl_summary.desP.ants_gt2d %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv_reg_data.tbl_summary.desP.ants_gt2d.docx")
```

@@

desP.ants_gt2d.quad.qb.tbl.merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv.reg_summary.desP.ants_gt2d.quad.docx")
```

@@

ggsave("desP.ant_treatment.quad.final.png",
       desP.ant_treatment.quad.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

@@

surv_reg_data.tbl_summary.desP.ant_treatment %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv_reg_data.tbl_summary.desP.ant_treatment.docx")
```

@@

desP.ant_treatment.quad.qb.tbl.merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv.reg_summary.desP.ant_treatment.quad.docx")
```

>>>>

ggsave(here("prelim_figs/Publilia-03-survivorship/",
            "desL.ant_treatment.quad.final.png"),
       desL.ant_treatment.quad.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

@@

surv_reg_data.tbl_summary.desL.ant_treatment %>%
  as_flex_table() %>%
  flextable::save_as_docx(path=here("prelim_figs/Publilia-03-survivorship/",
                                    "surv_reg_data.tbl_summary.desL.ant_treatment.docx"))
```

@@

desL.ant_treatment.quad.qb.tbl.merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path=here("prelim_figs/Publilia-03-survivorship/",
                                    "surv.reg_summary.desL.ants_treatment.quad.docx"))
```

@@

ggsave(here("prelim_figs/Publilia-03-survivorship/",
            "desL.ants_gt2d.quad.final.png"),
       desL.ants_gt2d.quad.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

@@

surv_reg_data.tbl_summary.desL.ants_gt2d %>%
  as_flex_table() %>%
  flextable::save_as_docx(path=here("prelim_figs/Publilia-03-survivorship/",
                                    "surv_reg_data.tbl_summary.desL.ants_gt2d.docx"))
```

@@

desL.ants_gt2d.quad.qb.tbl.merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path=here("prelim_figs/Publilia-03-survivorship/",
                                    "surv.reg_summary.desL.ants_gt2d.quad.docx"))
```

@@

ggsave(here("prelim_figs/Publilia-03-survivorship/",
            "desP.ants_gt2d.quad.final.png"),
       desP.ants_gt2d.quad.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

@@

surv_reg_data.tbl_summary.desP.ants_gt2d %>%
  as_flex_table() %>%
  flextable::save_as_docx(path=here("prelim_figs/Publilia-03-survivorship/",
                                    "surv_reg_data.tbl_summary.desP.ants_gt2d.docx"))
```

@@

desP.ants_gt2d.quad.qb.tbl.merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path=here("prelim_figs/Publilia-03-survivorship/",
                                    "surv.reg_summary.desP.ants_gt2d.quad.docx"))
```

@@

ggsave(here("prelim_figs/Publilia-03-survivorship/",
            "desP.ant_treatment.quad.final.png"),
       desP.ant_treatment.quad.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

@@

surv_reg_data.tbl_summary.desP.ant_treatment %>%
  as_flex_table() %>%
  flextable::save_as_docx(path=here("prelim_figs/Publilia-03-survivorship/",
                                    "surv_reg_data.tbl_summary.desP.ant_treatment.docx"))
```

@@

desP.ant_treatment.quad.qb.tbl.merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path=here("prelim_figs/Publilia-03-survivorship/",
                                    "surv.reg_summary.desP.ant_treatment.quad.docx"))
```
